Software Ticket Quality

### 2017-10-29 proposal/mprop.tex
Add paper on impact related to poor data quality
Finish paper on poor data quality in enterprise

>>>>

\textbf{Impact of Poor Data Quality}\cite{redman1998impact}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main purpose of the article is to provide some insights into how
    data quality can have a major economical impact on a company, as well
    as to raise awareness about this issue.
  \item \textbf{What was the method?}
    The author has analysed various large enterprises and their available data 
    to infer conclusions about the impact data quality has.
  \item \textbf{What did they learn?}
    There are three main issues across most enterprises:
      \begin{itemize}
        \item inaccurate data;
        \item inconsistencies across databases;
        \item unavailable data necessary for certain operations.
      \end{itemize}
    Moreover, the paper also presents a list of impacts poor data quality brings, among 
    which we can find:
      \begin{itemize}
        \item lowered customer satisfaction;
        \item increased cost;
        \item lowered employee satisfaction;
        \item it becomes more difficult to set strategy;
        \item poorer decision making.
      \end{itemize}
  \item \textbf{Relevance to our work}: this is a key paper on data quality in
    an enterprise setting and what impact it can have. It is valuable to our research 
    because we can relate the findings with what negative impacts poor tickets
    can bring to software projects.
\end{itemize}
